MS Keyrun Species, Environment, Data Formats

### 2020-07-30 docs/SpeciesEnvDat.Rmd
update with survey results

Responses:
```{r}
# each row is a response with a comma delimited list of species
# string split each row to species
# tally by species
# histogram

#msspecies <- responses$Species

@@

Responses:
```{r}
# each row is a response with a comma delimited list of environmental data
# string split each row to dataset name
# tally by dataset
# histogram

#msspecies <- responses$Environment

@@

@@

#useR <- data.frame(ModelinR = responses$ModelinR,

## Meeting minutes (old link)

[Click here!](https://docs.google.com/document/d/19FpJ8w2a-ZZ8ZY4ZmsnjlIilLeN1X9_Tz1dM-KsdOOw/edit#heading=h.kvnvc0pxyvqq)

>>>>

Responses:
```{r, fig.height=6}
# each row is a response with a comma delimited list of species
# string split each row to species
# tally by species
# histogram

msspecies <- data.frame(Species = responses$Species,
                        Model = c("MS", "MS", "NA", "MS", "Rpath", "MS")) %>%
  filter(Model != "NA") %>%
  separate_rows(Species, sep = ",") %>%
  mutate(Species = str_trim(Species, side = "both"))

ggplot(msspecies, aes(Species)) + 
  geom_bar() +
  facet_wrap(~Model, nrow = 2, scales="free") +
  theme(axis.text.x = element_text(angle = 90))

@@

Responses:
```{r, fig.height=10}
# each row is a response with a comma delimited list of environmental data
# string split each row to dataset name
# tally by dataset
# histogram

msenv <- data.frame(Environment = responses$Environment,
                        Model = c("MS", "MS", "NA", "MS", "Rpath", "MS")) %>%
  filter(Model != "NA") %>%
  separate_rows(Environment, sep = ",") %>%
  mutate(Environment = str_trim(Environment, side = "both"))

ggplot(msenv, aes(Environment)) + 
  geom_bar() +
  facet_wrap(~Model, nrow = 2, scales="free") +
  theme(axis.text.x = element_text(angle = 90))

@@

Many but not all models interface with R and can use R datasets. Even for those that do not, all agreed on using an R data package for standardizing input datasets and making them available.

@@

useR <- data.frame(ModelInR = responses$ModelInR,
                   ModelUseR = responses$ModelUseR,
                   RData = responses$RData) %>%
  gather(question, answer, ModelInR:RData) %>%
  mutate(shortans = ifelse(is.na(word(answer, 1, 2)), 
                           answer, 
                           word(answer, 1, 2)))

ggplot(useR, aes(question)) +
  geom_bar(aes(fill=shortans)) +
  labs(x = "Question", 
       fill = "Short Answer") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 35))

```
Short answer key:
"No but" = `r unique(useR$answer)[2]`  
"Probably, we" = `r unique(useR$answer)[4]`

## Meeting minutes, 5 August 2020

[Click here!](https://docs.google.com/document/d/19FpJ8w2a-ZZ8ZY4ZmsnjlIilLeN1X9_Tz1dM-KsdOOw/edit#heading=h.m573izndd2nh)
